R Notebook

### 2019-09-24 src/testing_file.Rmd
plotting for paper - error with names for depths

Threshold tables
```{r}
thlst1 <- list.files(paste0("../output/maxent/models"), pattern = ".*avgAIC.csv", full.names = TRUE)
thlst2 <- list.files(paste0("../output/maxent/models"), pattern = ".*avgmaxentresults.csv", full.names = TRUE)

>>>>

#Threshold tables
```{r}
thlst1 <- list.files(paste0("../output/maxent/models"), pattern = ".*avgAIC.csv", full.names = TRUE)
thlst2 <- list.files(paste0("../output/maxent/models"), pattern = ".*avgmaxentresults.csv", full.names = TRUE)
